Master's Project Journal

### 2019-02-18 tex_files/Journal.tex
ring osc network lock journal update

\section*{Gains}
Table \ref{table:sdf} contains the gains required to achieve locking, and in the case of the PA ADPLL, the most visually optimal jitter. I have not yet checked the ring on the better scope so the values may not in fact be optimal.
\begin{table}[!ht]
	\begin{center} 
		\begin{tabular}{c|c|c|c|c}           
			Configuration & $K_p$ Width & $K_p$ & $K_i$ Width & $K_i$ \\
			PA ADPLL (5 MHz) & 2.1 & 001  & 1.4 & 0001 \\
			PA ADPLL div8 & 1.4 & 1001 & 1.7 & 0001 \\
			PA Chained & 1.4 & 0001 & 1.8 & 0001 \\
			PA 2x2 & 1.5 & 1000 & 1.7 & 0001 \\
			RO ADPLL & 1.5 & 0111 & 1.7 & 0001 \\
			RO ADPLL div2/4 & 1001 & 1000 & 1.7 & 0001 \\
		\end{tabular}
		\caption{PA @ 10, RO @ 5}
		\label{table:sdf}
	\end{center}
\end{table}

\end{document}

>>>>

\section*{Gains}
Table \ref{table:sdf} contains the gains required to achieve locking, and in the case of the PA ADPLL, the most visually optimal jitter. I have not yet checked the ring on the better scope so the values may not in fact be optimal.
\begin{table}[!ht]
	\begin{center} 
		\begin{tabular}{c|c|c|c|c}           
			Configuration & $K_p$ Width & $K_p$ & $K_i$ Width & $K_i$ \\
			PA ADPLL (5 MHz) & 2.1 & 001  & 1.4 & 0001 \\
			PA ADPLL div8 & 1.4 & 1001 & 1.7 & 0001 \\
			PA Chained & 1.4 & 0001 & 1.8 & 0001 \\
			PA 2x2 & 1.5 & 1110 & 1.7 & 0001 \\
			RO ADPLL & 1.5 & 0111 & 1.7 & 0001 \\
			RO ADPLL div2/4 & 1001 & 1000 & 1.7 & 0001 \\
            RO 2x2 & 1.4 & 0100 & 1.7 & 0001 \\
		\end{tabular}
		\caption{PA @ 10, RO @ 5}
		\label{table:sdf}
	\end{center}
\end{table}

\section*{Ring Osc Locking}
After many trials and tribulations, including a situation where the ring adpll was locking to the inverse of the reference applied to it I finally managed to get the ring locked at 5 MHz with a 4 times divider. Turns out the shifting of $K_p$ and $K_i$ in the same direction did not help matters as I thought it might.
In fact increasing $K_p$ while decreasing $k_i$ turned out to be the solution to my problems.
Along the way I located an error where I was using 5'd16 as the bias which doesnt work with a subtraction of 15 to -16, as it would give overflow. Athough I had actually  made the counter the same in both directions so this didnt actually manifest itself as an issue.
The lock range is now heavily impacted by the gains as I discovered when attempting to copy gains from the PA ADPLL.
The key to solving it was going through all the fixed point arith. and checking that the widths made sense, which made my realise I had made a false assummtion that going from an 8 to a 5 bit detector/filter resulted in a div by eight times more at the exit of the filter, but in fact had the same div by 4.
After discovering this I had it locking within 3 hours of work, when prior I had spent ~ 9 days on the calendar and ~30 hours working on the problem. Locking perofmance looks potentially better than the 10 MHz perf of the ADPLL (magnitude not \% for the sake of comp. However div is by 4 now not 8, and res is twice as good.) In the coming week I will be characterising the perf of these different designs to compare effectively.
\end{document}
